国際会議発表

### 2025-07-18 presentation.Rmd
update

>>>>

### 2025

- [46] Kunisato, Y. & Warashina, K.(2025). The Influence of the Number of Latent Causes on Perceived Physical Threat in a Panic Network. Computational Psychiatry Conference 2025, July14-16, Tübingen.

### 2023

- [45] Omizu,T. & Kunisato, Y.(2023). Network simulation of depression as a complex system with treatment components. ALIFE 2023: Ghost in the Machine, July24-29, Sapporo. [link](https://doi.org/10.1162/isal_a_00612)

### 2021

- [44] Toyama, A. & Kunisato, Y. (2021). Characteristic learning process in insomnia. The 54th Annual Meeting of the Society for Mathematical Psychology, July 1-12, Virtual.
